Ecosystem carbon balance in the Hawaiian Islands under different scenarios of future climate and land use change

### 2020-07-22 Manuscript/HI_Model_ms.Rmd
modified bibtex, .csl, and manuscript files

---
title: "Ecosystem carbon balance in the Hawaiian Islands under different scenarios of future climate and land use change"
bibliography: HI_Model.bib
csl: environmental-research-letters.csl
fontsize: 12pt
geometry: margin=1in
header-includes:
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{setspace}
   - \doublespacing
output: 
  pdf_document: 
    latex_engine: xelatex
---

@@

## Methods
We used the Land Use and Carbon Scenario Simulator (LUCAS), an integrated landscape change and carbon gain-loss model, to project changes in ecosystem carbon balance for the seven main Hawaiian Islands under four scenarios incorporating different levels of climate and land-use change.

@@

```{r fig.align = 'center', out.width = "80%", fig.cap = "Land cover classification of the seven main Hawaiian Islands, adapted from Jacobi et al. (2017). Agriculture in this map combines herbaceous and woody crops, but these two crop types are treated as separate land cover classes in the simulation model. Water and Wetland land cover classes are not shown."}
knitr::include_graphics("./fig_images/fig1_HI_LC.png")
```

@@

>>>>

---
title: "Ecosystem carbon balance in the Hawaiian Islands under different scenarios of future climate and land use change"
bibliography: HI_Model.bib
csl: iop.csl
fontsize: 12pt
geometry: margin=1in
header-includes:
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{setspace}
   - \doublespacing
output: 
  pdf_document: 
    latex_engine: xelatex
urlcolor: blue
---

@@

## Methods
We used the Land Use and Carbon Scenario Simulator (LUCAS), an integrated landscape change and carbon gain-loss model, to project changes in ecosystem carbon balance for the seven main Hawaiian Islands under four scenarios of climate and land-use change. The landscape change portion of LUCAS is a state-and-transition model that applies a Monte Carlo approach to track the state type and age of each simulation cell in response to a pre-determined set of transitions [@daniel_state-and-transition_2016]. The carbon gain-loss portion of LUCAS tracks carbon stocks within each simulation cell over time as continuous state variables, as well as a pre-defined set of continuous flows specifying stock level rates of change over time [@daniel_integrating_2018]. The Hawai`i LUCAS model estimated the annual change in carbon stocks and fluxes in response to land use changes associated with urbanization, agricultural expansion and contraction, forest and agricultural harvesting, and wildland fire. We also estimated the impact of short- and long-term climate variability on net primary productivity and the turnover of dead organic matter [@sleeter_effects_2019].

@@

```{r fig.align = 'center', out.width = "80%", fig.cap = "Land cover classification of the seven main Hawaiian Islands, adapted from Jacobi et al (2017). Agriculture in this map combines herbaceous and woody crops, but these two crop types are treated as separate land cover classes in the simulation model. Water and Wetland land cover classes are not shown."}
knitr::include_graphics("./fig_images/fig1_HI_LC.png")
```

@@

## Data Availability

Tabular model output data are available from the USGS ScienceBase data repository at: https://doi.org/10.5066/P9AWLFKZ. Model input data and R code used to generate input data, summarize output data, and compile this manuscript are available from the HI_Model GitHub repository at: https://github.com/selmants/HI_Model.

## ORCID

Paul C. Selmants https://orcid.org/0000-0001-6211-3957

Benjamin M. Sleeter https://orcid.org/0000-0003-2371-9571

Jinxun Liu https://orcid.org/0000-0003-0561-8988

Tamara S. Wilson https://orcid.org/0000-0001-7399-7532

Abby G. Frazier https://orcid.org/0000-0003-4076-4577

Gregory P. Asner https://orcid.org/0000-0001-7893-6421

## References
